---
title: "Sentinel - 2"
subtitle: "Assessing one of the main satellites <br/>for Remote sensing"  
author: 
  - "Fiorella Guillen <br/> CASA0023" 
date: '`r Sys.Date()`'

output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: solarized-dark
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#2569e8",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF",
  title_slide_text_color = "#FFFFFF",
  title_slide_background_image = "images/Ecosystem_services_2.jpg",
  base_font_size = "22px"
)
```

```{css, echo=FALSE}
.left-column {
  width: 10%;
  padding-right: 10px;
}

.right-column {
  width: 85%;
}
```

## Key facts

* This satellite is managed by the **European Space Agency** and it's part of the **Copernicus Program**
* Launched on 2015, 2017 and 2024
* It's equiped with a **MultiSpectral Instrument (MSI)** that uses a push-broom **passive sensor** 

.left-column[
## ** 2**

## ** 5**

## ** 13** 
]

.right-column[
####Identical satellites -Sentinel 2A and 2B- flying <br/> the same orbit but phased at 180°####

####Days revisit frequency at the Equator <br/> (**high** revisit frequency)####

####Spectral bands including four bands at 10m, six bands <br/> at 20m and three bands at 60m spatial resolution####

]

---

## Resolutions

####Temporal resolution:####
Each satellite has a 10 days revisit frequency, but **combined** it has a **5 days revisit frequency**

####Spatial resolution:####
Depends on the particular spectral band, ranges from **10 to 60 m** spatial resolution
####Spectral resolution:####
Includes **13 spectral bands** that range from the Visible and Near Infrared to the Short Wave Infrared
####Radiometric resolution:####
The MSI instrument has a **12 bit resolution**, with a rave of 0 to 4095 potential light instensity values
---


---
class: inverse center middle

# Topic Changing Interstitial

---
class: center, middle

# Thanks!

Slides created via the R packages:

[**xaringan**](https://github.com/yihui/xaringan)<br>
[gadenbuie/xaringanthemer](https://github.com/gadenbuie/xaringanthemer)
